---
title: "Reportes"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("functions.R")

blood <- read_excel("data/Base de datos.xlsx")
```

# Proyecto: Sangre total -- FVL-2019/20
#### Statistics analysis: V.1.0 Date: 16-01-2020
#### @author: Edgar Yaset Caicedo -- https://github.com/yaset

## Hemoglobina

### Description
```{r , echo = FALSE }
Hb <- data_base("Hb")
round(resume(Hb),2)
```

### Prueba de ANOVA

```{r, echo= FALSE}
anova_te(Hb)
data2 <- resume(Hb)
ggplot( data = data2,mapping =  aes(x= time, y = mean))+
  geom_point(aes(y = mean))+
  geom_errorbar(aes(ymin = mean - es, ymax = mean + es), width = 2)+
  geom_line()+
  ylim(c(0,18))+
  xlab("Days")+
  ylab("Hemoglobin g/dL")+
  theme_bw()+
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text = element_text(size = 14))


```

## Hematocrito

### Description
```{r , echo = FALSE }
Hto <- data_base("Hcto")
round(resume(Hto),2)
```

### Prueba de ANOVA

```{r, echo= FALSE}
anova_te(Hto)
data2 <- resume(Hto)
ggplot( data = data2,mapping =  aes(x= time, y = mean))+
  geom_point(aes(y = mean))+
  geom_errorbar(aes(ymin = mean - es, ymax = mean + es), width = 2)+
  geom_line()+
  ylim(c(0,50))+
  xlab("Days")+
  ylab("Hematocrito")+
  theme_bw()+
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text = element_text(size = 14))


```

# Plaquetas


### Description
```{r , echo = FALSE }
Plt <- data_base("Plt")
round(resume(Plt),2)
```

### Prueba de ANOVA

```{r, echo= FALSE}
anova_te(Plt)
data2 <- resume(Plt)
ggplot( data = data2,mapping =  aes(x= time, y = mean))+
  geom_point(aes(y = mean))+
  geom_errorbar(aes(ymin = mean - es, ymax = mean + es), width = 2)+
  geom_line()+
  ylim(c(0,300000))+
  xlab("Days")+
  ylab("Plaquetas")+
  theme_bw()+
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text = element_text(size = 14))


```

# Fibrinogeno
### Description
```{r , echo = FALSE }
Fibri <- data_base("Fibri")
round(resume(Fibri),2)
```

### Prueba de ANOVA
```{r, echo= FALSE}
anova_te(Fibri)
data2 <- resume(Fibri)
ggplot( data = data2,mapping =  aes(x= time, y = mean))+
  geom_point(aes(y = mean))+
  geom_errorbar(aes(ymin = mean - es, ymax = mean + es), width = 2)+
  geom_line()+
  ylim(c(0,400))+
  xlab("Days")+
  ylab("Fibrinogeno")+
  theme_bw()+
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text = element_text(size = 14))
```

# Factor II
### Description
```{r , echo = FALSE }
FII <- data_base("FII")
round(resume(FII),2)
```

### Prueba de ANOVA
```{r, echo= FALSE}
anova_te(FII)
data2 <- resume(FII)
ggplot( data = data2,mapping =  aes(x= time, y = mean))+
  geom_point(aes(y = mean))+
  geom_errorbar(aes(ymin = mean - es, ymax = mean + es), width = 2)+
  geom_line()+
  ylim(c(0,100))+
  xlab("Days")+
  ylab("Factor II")+
  theme_bw()+
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text = element_text(size = 14))

```

# Factor V
### Description
```{r , echo = FALSE }
FV <- data_base("\\FV\\b")
round(resume(FV),2)
```

### Prueba de ANOVA
```{r, echo= FALSE}
anova_te(FV)
data2 <- resume(FV)
 ggplot( data = data2,mapping =  aes(x= time, y = mean))+
  geom_point(aes(y = mean))+
  geom_errorbar(aes(ymin = mean - es, ymax = mean + es), width = 2)+
  geom_line()+
  ylim(c(0,100))+
  xlab("Days")+
  ylab("Factor V")+
  theme_bw()+
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text = element_text(size = 14))

```

## Factor VII
### Description

```{r , echo = FALSE }
FVII <- data_base("\\FVII\\b")
round(resume(FVII),2)
```

### Prueba de ANOVA
```{r, echo= FALSE}
anova_te(FVII)
data2 <- resume(FVII)
 ggplot( data = data2,mapping =  aes(x= time, y = mean))+
  geom_point(aes(y = mean))+
  geom_errorbar(aes(ymin = mean - es, ymax = mean + es), width = 2)+
  geom_line()+
  ylim(c(0,100))+
  xlab("Days")+
  ylab("Factor VII")+
  theme_bw()+
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text = element_text(size = 14))

```


# Factor VIII
### Description
```{r , echo = FALSE }
FVIII <- data_base("\\FVIII\\b")
round(resume(FVII),2)
```

### Prueba de ANOVA
```{r, echo= FALSE}
anova_te(FVIII)
data2 <- resume(FVIII)
 ggplot( data = data2,mapping =  aes(x= time, y = mean))+
  geom_point(aes(y = mean))+
  geom_errorbar(aes(ymin = mean - es, ymax = mean + es), width = 2)+
  geom_line()+
  ylim(c(0,150))+
  xlab("Days")+
  ylab("Factor VIII")+
  theme_bw()+
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text = element_text(size = 14))

```


# Factor IX
### Description
```{r , echo = FALSE }
FIX <- data_base("\\FIX\\b")
round(resume(FIX),2)
```

### Prueba de ANOVA
```{r, echo= FALSE}
anova_te(FIX)
data2 <- resume(FIX)
 ggplot( data = data2,mapping =  aes(x= time, y = mean))+
  geom_point(aes(y = mean))+
  geom_errorbar(aes(ymin = mean - es, ymax = mean + es), width = 2)+
  geom_line()+
  ylim(c(0,150))+
  xlab("Days")+
  ylab("Factor IX")+
  theme_bw()+
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text = element_text(size = 14))

```


# Factor X
### Description
```{r , echo = FALSE }
FX <- data_base("\\FX\\b")
round(resume(FX),2)
```

### Prueba de ANOVA
```{r, echo= FALSE}
anova_te(FX)
data2 <- resume(FX)
 ggplot( data = data2,mapping =  aes(x= time, y = mean))+
  geom_point(aes(y = mean))+
  geom_errorbar(aes(ymin = mean - es, ymax = mean + es), width = 2)+
  geom_line()+
  ylim(c(0,150))+
  xlab("Days")+
  ylab("Factor X")+
  theme_bw()+
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text = element_text(size = 14))

```

# Factor XI
### Description
```{r , echo = FALSE }
FXI <- data_base("\\FXI\\b")
round(resume(FXI),2)
```

### Prueba de ANOVA
```{r, echo= FALSE}
anova_te(FXI)
data2 <- resume(FXI)
 ggplot( data = data2,mapping =  aes(x= time, y = mean))+
  geom_point(aes(y = mean))+
  geom_errorbar(aes(ymin = mean - es, ymax = mean + es), width = 2)+
  geom_line()+
  ylim(c(0,150))+
  xlab("Days")+
  ylab("Factor XI")+
  theme_bw()+
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text = element_text(size = 14))

```


# PCC
### Description
```{r , echo = FALSE }
PCC <- data_base("\\PCC\\b")
round(resume(PCC),2)
```

### Prueba de ANOVA
```{r, echo= FALSE}
anova_te(PCC)
data2 <- resume(PCC)
 ggplot( data = data2,mapping =  aes(x= time, y = mean))+
  geom_point(aes(y = mean))+
  geom_errorbar(aes(ymin = mean - es, ymax = mean + es), width = 2)+
  geom_line()+
  ylim(c(0,150))+
  xlab("Days")+
  ylab("PCC")+
  theme_bw()+
  theme(axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text = element_text(size = 14))

```
